Numerical experiment investigating the influence of drag on trajectory patterns of floating macroalgae

### 2021-05-10 thesis_chapter_3.Rmd
touchups

## Model inputs
## Ocean and wind model

@@

## Hydrodynamic and wind drag

@@

area_table <- read.csv("tables/chapter_3/area_table.csv", sep = ";")
area_table <- flextable(data = area_table)
area_table <- theme_zebra(area_table, odd_header = "transparent", even_header = "transparent")
area_table <- align(x= area_table, align = "center", part = "all")
area_table <- set_header_labels(area_table, Plant.characteristic = "Plant characteristic", Approximate.shape = "Approximate shape", Equation.used = "Equation Used", Plant.dimensions = "Plant dimensions")
area_table <- set_header_labels(area_table, Ac.Minimum = "Ac Minimum", Ac.Mean = "Ac Mean", Ac.Maximum = "Ac Maximum")
area_table <- set_table_properties(area_table, width = 1, layout = "autofit")
area_table <- fontsize(area_table, size = 8, part = "body")
area_table <- fontsize(area_table, size = 8, part = "header")
area_table <- set_caption(area_table, "Table 2: Table summarising the attributes and estimates used to calculate the overall surface area of Kommetjie kelp individuals used in the various simulations. Approximate shape refers to the dimensions of the geometric shape used to represent a particular morphological characteristic. Equations used are the equations relating to the dimensions used for the geometric shape estimate. Plant dimensions are the measurements used, collected in previous work by @coppin2020, used to calculate the associated surface areas. Ac refers to the cross-sectional area calculated. The total surface areas for each plant characteristic for each surface area type make up the remaining columns.")
area_table
```
## Analysis

@@

heatmap_RK4_acc <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = pass_acc_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Passive") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

heatmap_kelp_acc <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = kelp_acc_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Kelp") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

point_RK4_acc <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = pass_acc, aes(x = lon, y = lat, colour = age)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

point_kelp_acc <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = kelp_acc, aes(x = lon, y = lat, colour = age)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

@@

heatmap_RK4_acc_April <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_April, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = pass_acc_mean_April, aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

heatmap_kelp_acc_April <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_April, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = kelp_acc_mean_April,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

point_RK4_acc_April <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = pass_acc_April, aes(x = lon, y = lat, colour = age))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

point_kelp_acc_April <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = kelp_acc_April, aes(x = lon, y = lat, colour = age))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

@@

heatmap_RK4_acc_July <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = pass_acc_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

heatmap_kelp_acc_July <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = kelp_acc_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

point_RK4_acc_July <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = pass_acc_July, aes(x = lon, y = lat, colour = age))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

point_kelp_acc_July <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = kelp_acc_July, aes(x = lon, y = lat, colour = age))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

@@

heatmap_RK4_acc_Oct <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_Oct, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = pass_acc_mean_Oct, aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

heatmap_kelp_acc_Oct <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_Oct, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 720))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = kelp_acc_mean_Oct, aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

point_RK4_acc_Oct <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = pass_acc_Oct, aes(x = lon, y = lat, colour = age))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

point_kelp_acc_Oct <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = kelp_acc_Oct, aes(x = lon, y = lat, colour = age)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12))

@@

ggarrange(heatmap_RK4_acc, heatmap_kelp_acc,heatmap_RK4_acc_April, heatmap_kelp_acc_April, heatmap_RK4_acc_July, heatmap_kelp_acc_July, heatmap_RK4_acc_Oct, heatmap_kelp_acc_Oct, common.legend = TRUE, legend = c("bottom"), ncol = 2, nrow = 4, labels = c("January","", "April","","July","","October"), font.label = list(size = 12, face = "bold"), align = "hv")

ggsave(filename = "figure_9.jpg", plot = last_plot(), path = "figures/chapter_3/", height = 10, width = 10, scale = 1, dpi = 300)
```

>>>>

## Model inputs
### Ocean and wind model

@@

### Hydrodynamic and wind drag

@@

area_table <- read.csv("tables/chapter_3/area_table.csv", sep = ";")
area_table <- flextable(data = area_table)
area_table <- theme_zebra(area_table, odd_header = "transparent", even_header = "transparent")
area_table <- align(x= area_table, align = "center", part = "all")
area_table <- set_header_labels(area_table, Plant.characteristic = "Plant characteristic", Approximate.shape = "Approximate shape", Equation.used = "Equation Used", Plant.dimensions = "Plant dimensions")
area_table <- set_header_labels(area_table, Ac.Minimum = "Ac Minimum", Ac.Mean = "Ac Mean", Ac.Maximum = "Ac Maximum")
area_table <- set_table_properties(area_table, width = 1, layout = "autofit")
area_table <- fontsize(area_table, size = 8, part = "body")
area_table <- fontsize(area_table, size = 8, part = "header")
area_table <- set_caption(area_table, "Table 2: Table summarising the attributes and estimates used to calculate the overall surface area of Kommetjie kelp individuals used in the various simulations. Approximate shape refers to the dimensions of the geometric shape used to represent a particular morphological characteristic. Equations used are the equations relating to the dimensions used for the geometric shape estimate. Plant dimensions are the measurements used, collected in previous work by @coppin2020, used to calculate the associated surface areas. Ac refers to the cross-sectional area calculated. The total surface areas for each plant characteristic for each surface area type make up the remaining columns.")
area_table
```

## Analysis

@@

heatmap_RK4_acc <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 3000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = pass_acc_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Passive") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        plot.title = element_text(hjust = 0.5),
        element_blank())

heatmap_kelp_acc <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 3000)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = kelp_acc_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  ggtitle("Kelp") +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        plot.title = element_text(hjust = 0.5),
        element_blank())

point_RK4_acc <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = pass_acc, aes(x = lon, y = lat, colour = age)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

point_kelp_acc <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = kelp_acc, aes(x = lon, y = lat, colour = age)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

@@

heatmap_RK4_acc_April <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_April, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 3000))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = pass_acc_mean_April, aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

heatmap_kelp_acc_April <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_April, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 3000))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = kelp_acc_mean_April,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

point_RK4_acc_April <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = pass_acc_April, aes(x = lon, y = lat, colour = age))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

point_kelp_acc_April <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = kelp_acc_April, aes(x = lon, y = lat, colour = age))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

@@

heatmap_RK4_acc_July <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 3000))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = pass_acc_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

heatmap_kelp_acc_July <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_July, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 3000))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = kelp_acc_mean_July,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

point_RK4_acc_July <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = pass_acc_July, aes(x = lon, y = lat, colour = age))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

point_kelp_acc_July <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = kelp_acc_July, aes(x = lon, y = lat, colour = age))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  coord_cartesian(xlim = c(11, 20), ylim = c(-36, -26)) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

@@

heatmap_RK4_acc_Oct <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = pass_acc_Oct, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 3000))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = pass_acc_mean_Oct, aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

heatmap_kelp_acc_Oct <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = kelp_acc_Oct, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "viridis", limits = c(1, 3000))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  geom_path(data = kelp_acc_mean_Oct, aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Number of particles")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

point_RK4_acc_Oct <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = pass_acc_Oct, aes(x = lon, y = lat, colour = age))  +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

point_kelp_acc_Oct <- ggplot() +
  geom_contour(data = sa_bathy, aes(x = lon, y = lat, z = depth), colour = "grey") +
  geom_point(data = kelp_acc_Oct, aes(x = lon, y = lat, colour = age)) +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 0.4, colour = "black", fill = "grey") +
  #scale_fill_continuous(type = "viridis", limits = c(0, 30)) +
  labs(x = expression(Longitude*degree*S)) +
  labs(y = expression(Latitude*degree*E)) +
  guides(fill=guide_legend(title="Age")) +
  coord_fixed(ratio=1/1, xlim = c(11, 20), ylim = c(-36, -27)) + # fix the aspect ratio of plot
  theme_bw() +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12),
        element_blank())

@@

ggarrange(heatmap_RK4_acc, heatmap_kelp_acc,heatmap_RK4_acc_April, heatmap_kelp_acc_April, heatmap_RK4_acc_July, heatmap_kelp_acc_July, heatmap_RK4_acc_Oct, heatmap_kelp_acc_Oct, common.legend = TRUE, legend = c("bottom"), ncol = 2, nrow = 4, labels = c("January","", "April","","July","","October"), font.label = list(size = 12, face = "bold"), align = "hv", label.x = 0.2)

ggsave(filename = "figure_9.jpg", plot = last_plot(), path = "figures/chapter_3/", height = 10, width = 10, scale = 2, dpi = 300)
```

```{r age data outputs, warning=FALSE, echo=FALSE, message=FALSE, fig.cap="Figure 10: Comparison of particle age between passive and kelp accumulation scenarios 53-60. Age is represented in hours since release. For each season, passive particles are plotted on the left column and kelp particles in the right.", fig.height=8, fig.width=8}
